Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-05 article.tex
Page 2, Line 8: "...and representation of complex...", "...series reactions." -> sentence is poorly written, rewrite

Chemical Reaction Networks (CRNs) are a fundamental concept of modelling
in numerous fields including systems biology, biochemistry, chemical
engineering and epidemiology. They are comprised of a set of chemical
species or biological entities and representation of complex interaction
and transformation between them through a series reactions. These
systems can be modelled and simulated through multiple approaches:
deterministic Ordinary Differential Equations (ODEs) to model
macroscopic behavior, Stochastic Differential Equations (SDEs) to model
microscopic fluctuations, and jump processes (Gillespie-like
simulations) to account for the discreteness of populations. Instead of
directly writing the equations for each of these formulations which is
error-prone and difficult to reuse, these models can be written in a
higher-level description that can be compiled for these different types
of simulations.

>>>>

Chemical Reaction Networks (CRNs) are a fundamental concept of modelling
in numerous fields including systems biology, biochemistry, chemical
engineering and epidemiology. They are comprised of a set of chemical
species or biological entities
and a set of reactions that mediate transformations between them. These
systems can be modelled and simulated through multiple approaches:
deterministic Ordinary Differential Equations (ODEs) to model
macroscopic behavior, Stochastic Differential Equations (SDEs) to model
microscopic fluctuations, and jump processes (Gillespie-like
simulations) to account for the discreteness of populations. Instead of
directly writing the equations for each of these formulations which is
error-prone and difficult to reuse, these models can be written in a
higher-level description that can be compiled for these different types
of simulations.
